A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-09-08 src/paper.tex
Algumas modificações na seção de design dos web services
Web services design and implementation finished

\section{Secondary Screen Implementation}

@@

A open source web framework~\cite{Walls2011} was used to develop the server side of the architecture, i.e., the web application. This framework facilitates the development of the front controller pattern in web-based application. Thus, all the requests are tunneled through a single entry point, which is an efficient mechanism to implement an API to access the web services. This mechanism not only routes and dispatches the requests to appropriate handlers, but also exposes a flexible and scalable API structure, which can be consumed by second screen devices using different programming languages.

@@

>>>>

\section{Implementation of the Secondary Screen Architecture}

@@

The second screen devices and the iTV terminals need to communicate with the web application in order to send viewer's interactions and retrieve content from the server. As defined in the Section~\ref{ssub_web_application}, this communication occurs by means of HTTP requests to the web services of the web application. Thus, an API containing the Uniform Resource Identifiers (URIs) and the HTTP methods available for each URI is needed.

\begin{table}
	\caption{Strategies to perform HTTP requests by combining URIs and HTTP methods.}
	\label{table_web_serv_design}
	\centering
	\begin{tabular}{|m{1.5cm}|>{\centering}m{1cm}|m{5cm}|}
	\hline
	\textbf{URI}&\textbf{HTTP method}&\textbf{Description of the operation}\tabularnewline
	\hline
	/resources & GET & Retrieves a collection of resources of the same type that is specified in the URI. \tabularnewline
	\hline
	/resources/\{id\} & GET & Retrieves a single resource identified by a given \emph{\{id\}}.\tabularnewline
	\hline
	/resources & POST & Creates a new resource of the same type that is specified in the URI.\tabularnewline
	\hline
	/resources/\{id\} & PUT & Updates a resource identified by a given \emph{\{id\}}.\tabularnewline
	\hline
	/resources/\{id\} & DELETE & Deletes a resource identified by a given \emph{\{id\}}.
	\tabularnewline
	\hline
	\end{tabular}
\end{table}

Table~\ref{table_web_serv_design} describes how the web services API are designed by combining URIs and HTTP methods. The URI specifies the resource of interest and the HTTP method indicates the desired action to be performed on the resource. Since each HTTP method is intended for a different purpose, it is necessary to identify what actions apply to each resource.

A open source web framework~\cite{Walls2011} was used to develop the server side of the architecture, i.e., the web services. This framework facilitates the development of the front controller pattern in web-based application. Thus, all the requests are tunneled through a single entry point, which is an efficient mechanism to implement an API to access the web services. This mechanism not only routes and dispatches the requests to appropriate handlers, but also exposes a flexible and scalable API structure, which can be consumed by second screen devices using different programming languages.

@@

Since there is a well-defined web services API to access resources in the web application, it is possible to send HTTP requests from second screen devices and iTV terminals. A base URI which contains the domain of the web application (e.g., \emph{http://example.com}) is used as part of the API. Thus, the implementation of the HTTP requests in the client devices must use the entire URI, including the resource of interest.

The effect of the HTTP request depends on the type of HTTP method that is used, which typically can be GET, POST, PUT, or DELETE. Requests using GET must only retrieve data from the server. Depending on the URI, a request using GET should retrieve either a single element or a collection of elements of the specified resource. Requests using POST demand that the server accept a new resource identified by the URI. Requests using PUT modify a resource identified by the URI. The requests using the DELETE method are intended to delete a resource specified by the URI.

The proper combination of URIs and HTTP methods is used to manipulate resources in HTTP requests. It is possible to implement CRUD (create, read, update and delete) operations that are intended for communication between the second screen devices and the web application. As a result, the client devices can consume the web services and perform the desired actions on the resources.As an example, a request can be used to send viewers' interactions to the web server, or to retrieve content that is personalized according past interactions of the viewer.
